Cross Validation Approaches for Penalized Cox Regression

### 2023-08-14 sub/smimr/response.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin = 1in]{geometry}
\usepackage{enumitem}
\usepackage{color}
\usepackage{amssymb,amsmath}
\usepackage{hyperref}
\hypersetup{colorlinks=true, citecolor=black, urlcolor=cyan}

@@

  Obviously, it also selects fewer false positives as well. However, since there is no objectively correct answer to the balance between false positives and false negatives that a model should include, there is no way to decide upon these methods by comparing TPR/NPR/PPV/etc. There are, however, objective measures of prediction accuracy, which demonstrate that V\&VH stops too early -- this is point of Section 3.1.

  To summarize, the logic of our presentation is: V\&VH stops too early (Section 3.1). What are the consequences of this? It misses true positives (Section 3.2).

\item Did the authors make the software available for the proposed approaches?

  \re Yes; the proposed cross-validated linear predictor approach is implemented in the \textbf{ncvreg} package. The basic approach and the Verweij and Van Houwelingen's approach are implemented in the \textbf{glmnet} package. The code to reproduce our simulations and analyses are available at \url{https://github.com/biydai/Cross-Validation}; this repository is currently private, with the expectation of making it public once the paper is accepted.

@@

\item Many places require major/minor clarification and corrections.

  \re Thank you very much for catching and pointing out all of these issues! We truly appreciate your attention to detail in reading our work. All of them have been fixed in the revised version of the manuscript. Most of these points don't need any comment (we simply adopted your recommendation). The only exception is your comment ``Equation (6) and P8L10: I found the definition of $\hat{\eta}^{\text{cv}}$ confusing. Do we not need some step for pooling cross-validated linear predictors over all K folds?'' To which our reply is that no additional steps are needed; the linear predictors are simply concatenated in order to obtain the vector of cross-validated linear predictors, as shown in Figure 1. Each fold produces $n/K$ entries; at the end of all $K$ folds, we have all $n$ elements of the cross-validated linear predictor. We have made this more explicit in the text after equation (8).

\end{enumerate}
\end{document}

### 2023-08-14 main.tex
Done with reviewer response

In the Cox model, the hazard function for subject $i$ is given by 
\begin{equation*}
  h_{i}(t) = h_{0}(t) \exp( X_{i}\Tr\bbeta),
\end{equation*} 
where $\bbeta$ is the coefficient vector for the model and $h_{0}$ is the baseline hazard and $\exp(X_i\Tr\bbeta)$ is the risk for a subject with covariates $X_i$ relative to that baseline.  The estimation of the coefficients is obtained by maximizing a partial likelihood.  Letting $t_i$ denote the time on study for subject $i$ and $\delta_{i}$ indicate whether or not an event is observed for subject $i$, each subject's individual contribution to that partial likelihood is
\begin{equation}
  \label{eq:cox-pl-subj}
  L_{i}(\bbeta) = \left \{\frac{\exp ( X_{i}\Tr\bbeta)}{\sum_{ k \in R(t_{i})}\exp ( X_{k}\Tr \bbeta)}\right \}^{\delta_{i}},
\end{equation}
where $R(t_{i})$ denotes the set of subjects at risk at time $t_{i}$.  The partial likelihood for the entire sample of $n$ subjects is then given by:
\begin{equation}
  \label{eq:cox-pl-sum}
  L(\bbeta) =\prod_{i = 1}^{n} L_{i}(\bbeta).
\end{equation}
Cox regression can be extended by introducing a penalty into the partial likelihood.  In penalized Cox regression, $\bbeta$ coefficient estimates are obtained by minimizing the objective function
\begin{equation}
  \label{eq:obj}
  Q(\bbeta) = - \frac{1}{n} \log L(\bbeta) + P_{\lambda}(\bbeta),
\end{equation}
where $P_{\lambda}(\bbeta)$ is a penalty function that depends on a regularization parameter $\lam$.  Throughout, we will assume without loss of generality that the covariates have been standardized such that $\sum_i x_{ij} = 0$ and $\tfrac{1}{n}\sum_i x_{ij}^2=1$.  This is standard practice in penalized regression to ensure that the penalization has the same effect for all covariates and is invariant to changes of location and scale.  The estimates are then converted back to the original scale after the model has been fit.  Centering the predictors is also standard in Cox regression to ensure that the baseline hazard is invariant to location shifts of the covariates.

@@

The fundamental challenge of conducting cross validation for Cox regression is that the baseline hazard is not estimated from the model, which prevents us from calculating prediction errors (residuals).  However, if one takes additional steps to estimate the baseline hazard in addition to estimating the regression coefficients, then such residuals can be calculated.  The deviance residual, a normalized form of the Martingale residual \citep{Therneau1990}, is a natural candidate for quantifying prediction error to use in quantifying the cross-validation error. Originally proposed for model diagnostics, deviance residuals have also been used as a predictive accuracy measure, particularly in the random survival forest literature \citep{LeBlanc1992, Ishwaran2004}. In the Cox model, the Martingale residuals $\{m_i\}_{i=1}^n$ and deviance residuals $\{d_i\}_{i=1}^n$ are given by
\begin{align}
  \label{eq:res-m}
  m_{i} &= \delta_{i} - H_{0}(t_{i})\exp(X_i\Tr\bbeta), \\
  \label{eq:res-d}
  d_{i} &= \text{sign}(m_{i})\sqrt{-2(m_i + \delta_{i}\log(\delta_{i} - m_i))}.  
\end{align}
where $H_0$ is the cumulative baseline hazard.

@@

Both of the cross-validation approaches in Section~\ref{Sec:cox-cv-existing} consist of adding together log partial likelihood measures from each fold.  An alternative method is to obtain linear predictors for each fold, then combine these linear predictors to calculate a partial likelihood. We refer to this method as the \emph{cross-validated linear predictors} approach. To be more specific, we would first obtain $\hat{\bbeta}^{-k}$ from training set $T_{k}$; then the cross-validated linear predictors can be calculated for each observation $i$ from the test set $D_k$:  
\begin{equation}
  \label{eq:cv-lp}
  \hat{\eta}^{\text{cv}}_{i} = X_{i}\Tr\hat{\bbeta}^{-k}
\end{equation} 
After repeating this for all K folds, a complete set of cross-validated linear predictors $\hat{\boldeta}^{\text{cv}} = ( \hat{\eta}^{\text{cv}}_{1},  \hat{\eta}^{\text{cv}}_{2} , ...  \hat{\eta}^{\text{cv}}_{n})$ for the whole sample is obtained. A partial likelihood can then be built using this set of linear predictors to evaluate the predictive accuracy of the model:
\begin{equation*}
  L(\hat{\boldeta}^{\text{cv}}) = \prod_{i=1}^{n} \left\{ \frac{\exp (\hat{\eta}^{\text{cv}}_{i})}{\sum_{\tau \in R(t_{i})}\exp (\hat{\eta}^{\text{cv}}_\tau)} \right\} ^{\delta_i}.
\end{equation*}
We define the cross-validation error evaluated with cross-validated linear predictors to be $$\CVE = - 2 \log L(\hat{\boldeta}^{\text{cv}}).$$

@@

Simulation studies were conducted to compare how the methods described in Section~\ref{Sec:methods} behave relative to each other in selecting the tuning parameter $\lambda$ and the corresponding model for LASSO penalized regression. For these simulation studies, the covariate matrix $X$, consisting of $n$ observations and $p$ covariates, was generated from independent $\text{Normal}(0, 1)$ samples. Given $X_i$ and a coefficient vector $\bbeta$, survival times were generated from an exponential distribution with rate parameter $\exp(X_i \Tr \bbeta)$. Censoring status indicators were drawn independently from the binomial distribution. All simulations were implemented in R \citep{R}.

@@

We also measure the predictive accuracy via the mean squared prediction error, or Brier score \citep{VanHouwelingen2011}. Let $\hat{S}(t_0|\lambda,x)$ denote the predicted probability for an individual with covariates $x$ to survive beyond time $t_0$, and let $y(t_0) = \mathbb{1}\left\{ t > t_{0}\right\}$ indicate whether the individual actually survived beyond time $t_0$. Then the Brier score is defined to be
\begin{equation}
\text{Brier}(y(t_0), \hat{S}(t_0|\lambda,x)) = (y(t_0) - \hat{S}(t_0|\lambda,x))^2.
\end{equation}
In our simulation study, for each data set, we generated another independent data set with 1000 uncensored observations. We computed Brier scores for all of the cross-validation methods for all individuals in this test set, setting $t_0$ to the median survival time.

The third measure we used is the Kullback-Leibler score, which measures the log-likelihood of the prediction model evaluated at the observations \citep{VanHouwelingen2011}. With the same notation defined in the previous paragraph, the Kullback-Leibler score is defined to be
\begin{equation}
	\text{KL}(y(t_0), \hat{S}(t_0|\lambda,x)) = -\left\{ y(t_0)\log(\hat{S}(t_0|\lambda,x) + (1 - y(t_0))\log(1 - \hat{S}(t_0|\lambda,x)) \right\}.
\end{equation}
As for the Brier score, KL scores were computed for all CV approaches at the median survival time.  Results were then averaged over the N replications. For both Brier and KL scores, a smaller score represents smaller prediction error, thus indicating better prediction accuracy.

@@

\caption{\label{Tab:sim} Comparing the predictive accuracy of four cross-validation methods under scenarios with varying dimension and signal strength}
\centering
\begin{tabular}[t]{lccccc}
\toprule
 Method & $\lambda$ & log(MSE Ratio) &Brier Score & Kullback Leibler & C Index\\
\midrule
&\multicolumn{5}{c}{\textbf{Scenario 1}: n = 150, p = 50, 5 non-zero features, weak signal}\\
\cline{2-6}
V\&VH  & 0.098 (0.030) & 1.561 (0.851) & 0.245 (0.014) & 0.685 (0.030) & 0.610 (0.035) \\
Basic  & 0.088 (0.025) & 1.531 (0.838) & 0.244 (0.013) & 0.683 (0.029) & 0.614 (0.029) \\
LinearPred  & 0.092 (0.029) & 1.543 (0.846) & 0.245 (0.014) & 0.684 (0.030) & 0.612 (0.034) \\
DevResid  & 0.098 (0.029) & 1.547 (0.848) & 0.245 (0.014) & 0.684 (0.030) & 0.611 (0.035) \\
\addlinespace
&\multicolumn{5}{c}{\textbf{Scenario 2}: n = 150, p = 50, 5 non-zero features, strong signal}\\
\cline{2-6}
V\&VH  & 0.071 (0.010) & 1.586 (0.989) & 0.176 (0.011) & 0.526 (0.027) & 0.750 (0.012) \\
Basic  & 0.066 (0.011) & 1.544 (0.971) & 0.176 (0.011) & 0.526 (0.028) & 0.749 (0.013) \\
LinearPred  & 0.067 (0.010) & 1.540 (0.981) & 0.176 (0.011) & 0.525 (0.028) & 0.750 (0.012) \\
DevResid  & 0.094 (0.011) & 1.995 (0.841) & 0.181 (0.011) & 0.539 (0.026) & 0.751 (0.013) \\
\addlinespace
&\multicolumn{5}{c}{\textbf{Scenario 3}: n = 400, p = 10000, 20 non-zero features, weak signal}\\
\cline{2-6}
V\&VH  & 0.126 (0.019) & 2.958 (0.416) & 0.251 (0.012) & 0.696 (0.026) & 0.589 (0.044) \\
Basic  & 0.103 (0.022) & 2.880 (0.437) & 0.244 (0.015) & 0.680 (0.031) & 0.603 (0.039) \\
LinearPred  & 0.105 (0.023) & 2.886 (0.437) & 0.244 (0.015) & 0.681 (0.031) & 0.602 (0.039) \\
DevResid  & 0.107 (0.022) & 2.895 (0.433) & 0.245 (0.014) & 0.683 (0.03) & 0.602 (0.039) \\
\addlinespace
&\multicolumn{5}{c}{\textbf{Scenario 4}: n = 400, p = 10000, 20 non-zero features, strong signal}\\
\cline{2-6}
V\&VH  & 0.084 (0.012) & 3.799 (0.548) & 0.176 (0.03) & 0.528 (0.069) & 0.763 (0.048) \\
Basic  & 0.059 (0.007) & 3.455 (0.578) & 0.154 (0.019) & 0.468 (0.049) & 0.780 (0.031) \\
LinearPred  & 0.060 (0.007) & 3.479 (0.574) & 0.155 (0.019) & 0.470 (0.049) & 0.780 (0.030) \\
DevResid  & 0.076 (0.018) & 3.708 (0.518) & 0.166 (0.024) & 0.502 (0.057) & 0.772 (0.049) \\
\bottomrule
\end{tabular}
\end{table}

@@

%\begin{figure}[h]
%	\centering
%	\begin{minipage}[t]{10cm}
%	\begin{algorithm}[H]
%	\caption{Standard Method}
%	\For{k in 1 to K } 
%	{
%		 Fit Cox Regression on $T_{k}$: Obtain model estimates $\hat{\beta}^{-k}$\;
%		 Evaluate the partial likelihood of $\hat{\beta}^{-k}$ on $D_{k}$: $l^{k}(\hat{\beta}^{-k})$\;		
%	} 
%	
%	$ CVE_{st} = - \sum_{k = 1}^{K} l^{k}(\hat{\beta}^{-k})$
% 	\end{algorithm}
%
%	\begin{algorithm}[H]
%  	 \caption{Verweij and Van Houwelingen's Method}
%	\For{k in 1 to K } 
%	{
%		 Fit Cox Regression on $T_{k}$:  Obtain model estimates $\hat{\beta}^{-k}$\;
%		 Evaluate the partial likelihood of $\hat{\beta}^{-k}$ on $T_{k}$: $l^{-k}(\hat{\beta}^{-k})$\;
%		 Evaluate the partial likelihood of $\hat{\beta}^{-k}$ on $D$: $l(\hat{\beta}^{-k})$\;
%		 Take the difference: $ l(\hat{\beta}^{-k}) - l^{-k}(\hat{\beta}^{-k}) $\;
%	} 
%
%	$ CVE_{vvh} = - \sum_{k = 1}^{K} \left\{ l(\hat{\beta}^{-k}) - l^{-k}(\hat{\beta}^{-k}) \right\}$
%	\end{algorithm}
%
%	\begin{algorithm}[H]
%    	\caption{Cross-Validated Linear Predictors}
%	\For{k in 1 to K } 
%	{
%		 Fit Cox Regression on $T_{k}$:  Obtain model estimates $\hat{\beta}^{-k}$\;
%		$\forall$ $ i$ subject in $D_k$: $\hat{\eta}_{i}^{-} = X_{i}\hat{\beta}^{-k}$\;
%	} 
%
%	$ CVE_{lp} = - l(\hat{\eta}^{-})$
%	\end{algorithm}
%	
%	\begin{algorithm}[H]
%   	\caption{Sums of Squared Deviance Residuals}
%	\For{k in 1 to K } 
%	{
%		Fit Cox Regression on $T_{k}$:  Obtain model estimates $\hat{\beta}^{-k}$\;
%		$\forall$ $ i$ subject in $D_k$: $\hat{\eta}_{i}^{-} = X_{i}\hat{\beta}^{-k}$\;
%	} 
%	Compute baseline hazard $\hat{\Lambda}_{0}$ based on $\hat{\eta}^{-}$\;
%	$\forall$ $ i$ subject $\in \left\{1,2,...,n\right\}$, compute:
%		\par\hspace{0.5cm} $\hat{M_{i}} = \delta_{i} -\hat{\Lambda}_{0}(t_{i})e^{\hat{\eta}^{-}_{i}}$;
%		\par\hspace{0.5cm} $d_{i} = sgn(\hat{M}_{i})(-2(\hat{M}_{i} + \delta_{i}log(\delta_{i} - \hat{M}_{i})))^{1/2}$;
%	$ CVE_{dr} = \sum_{i = 1}^{n} {d}_{i}^2$ \;
%	\end{algorithm}
%	\end{minipage}
%	\caption{Pseudo Code for Cross-validation Procedures}
%	\end{figure}

>>>>

In the Cox model, the hazard function for subject $i$ is given by 
\begin{equation*}
  h_{i}(t) = h_{0}(t) \exp( \x_i\Tr\bbeta),
\end{equation*} 
where $\bbeta$ is the coefficient vector for the model and $h_{0}$ is the baseline hazard and $\exp(\x_i\Tr\bbeta)$ is the risk for a subject with covariates $\x_i$ relative to that baseline.  The estimation of the coefficients is obtained by maximizing a partial likelihood.  Letting $t_i$ denote the time on study for subject $i$ and $\delta_{i}$ indicate whether or not an event is observed for subject $i$, each subject's individual contribution to that partial likelihood is
\begin{equation}
  \label{eq:cox-pl-subj}
  L_{i}(\bbeta) = \left \{\frac{\exp ( \x_i\Tr\bbeta)}{\sum_{ k \in R(t_{i})}\exp (\x_k \Tr \bbeta)}\right \}^{\delta_{i}},
\end{equation}
where $R(t_{i})$ denotes the set of subjects at risk at time $t_{i}$.  The partial likelihood for the entire sample of $n$ subjects is then given by:
\begin{equation}
  \label{eq:cox-pl-sum}
  L(\bbeta) =\prod_{i = 1}^{n} L_{i}(\bbeta).
\end{equation}
Cox regression can be extended by introducing a penalty into the partial likelihood.  In penalized Cox regression, $\bbeta$ coefficient estimates are obtained by minimizing the objective function
\begin{equation}
  \label{eq:obj}
  Q(\bbeta) = - \frac{1}{n} \log L(\bbeta) + P_{\lambda}(\bbeta),
\end{equation}
where $P_{\lambda}(\bbeta)$ is a penalty function that depends on a regularization parameter $\lam$.  Throughout, we will assume without loss of generality that the covariates have been standardized such that $\sum_i x_{ij} = 0$ and $\tfrac{1}{n}\sum_i x_{ij}^2=1$.  This is standard practice in penalized regression to ensure that the penalization has the same effect for all covariates and is invariant to changes of location and scale.  The estimates are then converted back to the original scale after the model has been fit.  Centering the predictors is also standard in Cox regression to ensure that the baseline hazard is invariant to location shifts of the covariates.

@@

The fundamental challenge of conducting cross validation for Cox regression is that the baseline hazard is not estimated from the model, which prevents us from calculating prediction errors (residuals).  However, if one takes additional steps to estimate the baseline hazard in addition to estimating the regression coefficients, then such residuals can be calculated.  The deviance residual, a normalized form of the Martingale residual \citep{Therneau1990}, is a natural candidate for quantifying prediction error to use in quantifying the cross-validation error. Originally proposed for model diagnostics, deviance residuals have also been used as a predictive accuracy measure, particularly in the random survival forest literature \citep{LeBlanc1992, Ishwaran2004}. In the Cox model, the Martingale residuals $\{m_i\}_{i=1}^n$ and deviance residuals $\{d_i\}_{i=1}^n$ are given by
\begin{align}
  \label{eq:res-m}
  m_{i} &= \delta_{i} - H_{0}(t_{i})\exp(\x_i\Tr\bbeta), \\
  \label{eq:res-d}
  d_{i} &= \text{sign}(m_{i})\sqrt{-2(m_i + \delta_{i}\log(\delta_{i} - m_i))}.  
\end{align}
where $H_0$ is the cumulative baseline hazard.

@@

Both of the cross-validation approaches in Section~\ref{Sec:cox-cv-existing} consist of adding together log partial likelihood measures from each fold.  An alternative method is to obtain linear predictors for each fold, then combine these linear predictors to calculate a partial likelihood. We refer to this method as the \emph{cross-validated linear predictors} approach. To be more specific, we would first obtain $\hat{\bbeta}^{-k}$ from training set $T_{k}$; then the cross-validated linear predictors can be calculated for each observation $i$ from the test set $D_k$:  
\begin{equation}
  \label{eq:cv-lp}
  \hat{\eta}^{\text{cv}}_{i} = \x_i\Tr\hat{\bbeta}^{-k}
\end{equation} 
After repeating this for all K folds, a complete set of cross-validated linear predictors $\hat{\boldeta}^{\text{cv}} = ( \hat{\eta}^{\text{cv}}_{1},  \hat{\eta}^{\text{cv}}_{2} , ...  \hat{\eta}^{\text{cv}}_{n})$ for the whole sample is obtained. A partial likelihood can then be built using this set of linear predictors to evaluate the predictive accuracy of the model:
\begin{equation*}
  L(\hat{\boldeta}^{\text{cv}}) = \prod_{i=1}^{n} \left\{ \frac{\exp (\hat{\eta}^{\text{cv}}_{i})}{\sum_{r \in R(t_{i})}\exp (\hat{\eta}^{\text{cv}}_r)} \right\} ^{\delta_i}.
\end{equation*}
We define the cross-validation error evaluated with cross-validated linear predictors to be $$\CVE = - 2 \log L(\hat{\boldeta}^{\text{cv}}).$$

@@

Simulation studies were conducted to compare how the methods described in Section~\ref{Sec:methods} behave relative to each other in selecting the tuning parameter $\lambda$ and the corresponding model for LASSO penalized regression. For these simulation studies, the covariate matrix $X$, consisting of $n$ observations and $p$ covariates, was generated from independent $\text{Normal}(0, 1)$ samples. Given $\x_i$ and a coefficient vector $\bbeta$, survival times were generated from an exponential distribution with rate parameter $\exp(\x_i \Tr \bbeta)$. Censoring status indicators were drawn independently from the binomial distribution. All simulations were implemented in R \citep{R}.

@@

We also measure the predictive accuracy via the mean squared prediction error, or Brier score \citep{VanHouwelingen2011}. Let $\hat{S}(t_0|\lambda,x)$ denote the predicted probability for an individual with covariates $x$ to survive beyond time $t_0$, and let $y(t_0) = \mathbb{1}\left\{ t > t_{0}\right\}$ indicate whether the individual actually survived beyond time $t_0$. Then the Brier score is defined to be
\begin{equation}
\text{Brier}(y(t_0), \hat{S}(t_0|\lambda, \x)) = \{ y(t_0) - \hat{S}(t_0|\lambda, \x) \}^2.
\end{equation}
In our simulation study, for each data set, we generated another independent data set with 1000 uncensored observations. We computed Brier scores for all of the cross-validation methods for all individuals in this test set, setting $t_0$ to the median survival time.

The third measure we used is the Kullback-Leibler score, which measures the log-likelihood of the prediction model evaluated at the observations \citep{VanHouwelingen2011}. With the same notation defined in the previous paragraph, the Kullback-Leibler score is defined to be
$$ \text{KL}(y(t_0), \hat{S}(t_0|\lambda, \x)) = -\left\{ y(t_0)\log(\hat{S}(t_0|\lambda, \x) + (1 - y(t_0))\log(1 - \hat{S}(t_0|\lambda, \x)) \right\}. $$
As for the Brier score, KL scores were computed for all CV approaches at the median survival time.  Results were then averaged over the N replications. For both Brier and KL scores, a smaller score represents smaller prediction error, thus indicating better prediction accuracy.

@@

\caption{\label{Tab:sim} Predictive accuracy of four cross-validation methods under scenarios with varying dimension and signal strength (standard deviations given in parentheses).}
\centering
\begin{tabular}[t]{lccccc}
\toprule
 Method & $\lambda$ & log(MSE Ratio) &Brier Score & Kullback Leibler & C Index\\
\midrule
&\multicolumn{5}{c}{\textbf{Scenario 1}: n = 150, p = 50, 5 non-zero features, weak signal}\\
\cline{2-6}
V\&VH  & 0.098 (0.030) & 1.561 (0.851) & 0.245 (0.014) & 0.685 (0.030) & 0.610 (0.035) \\
Basic  & 0.088 (0.025) & 1.531 (0.838) & 0.244 (0.013) & 0.683 (0.029) & 0.614 (0.029) \\
LinearPred  & 0.092 (0.029) & 1.543 (0.846) & 0.245 (0.014) & 0.684 (0.030) & 0.612 (0.034) \\
DevResid  & 0.098 (0.029) & 1.547 (0.848) & 0.245 (0.014) & 0.684 (0.030) & 0.611 (0.035) \\
\addlinespace
&\multicolumn{5}{c}{\textbf{Scenario 2}: n = 150, p = 50, 5 non-zero features, strong signal}\\
\cline{2-6}
V\&VH  & 0.071 (0.010) & 1.586 (0.989) & 0.176 (0.011) & 0.526 (0.027) & 0.750 (0.012) \\
Basic  & 0.066 (0.011) & 1.544 (0.971) & 0.176 (0.011) & 0.526 (0.028) & 0.749 (0.013) \\
LinearPred  & 0.067 (0.010) & 1.540 (0.981) & 0.176 (0.011) & 0.525 (0.028) & 0.750 (0.012) \\
DevResid  & 0.094 (0.011) & 1.995 (0.841) & 0.181 (0.011) & 0.539 (0.026) & 0.751 (0.013) \\
\addlinespace
&\multicolumn{5}{c}{\textbf{Scenario 3}: n = 400, p = 10000, 20 non-zero features, weak signal}\\
\cline{2-6}
V\&VH  & 0.126 (0.019) & 2.958 (0.416) & 0.251 (0.012) & 0.696 (0.026) & 0.589 (0.044) \\
Basic  & 0.103 (0.022) & 2.880 (0.437) & 0.244 (0.015) & 0.680 (0.031) & 0.603 (0.039) \\
LinearPred  & 0.105 (0.023) & 2.886 (0.437) & 0.244 (0.015) & 0.681 (0.031) & 0.602 (0.039) \\
DevResid  & 0.107 (0.022) & 2.895 (0.433) & 0.245 (0.014) & 0.683 (0.03) & 0.602 (0.039) \\
\addlinespace
&\multicolumn{5}{c}{\textbf{Scenario 4}: n = 400, p = 10000, 20 non-zero features, strong signal}\\
\cline{2-6}
V\&VH  & 0.084 (0.012) & 3.799 (0.548) & 0.176 (0.03) & 0.528 (0.069) & 0.763 (0.048) \\
Basic  & 0.059 (0.007) & 3.455 (0.578) & 0.154 (0.019) & 0.468 (0.049) & 0.780 (0.031) \\
LinearPred  & 0.060 (0.007) & 3.479 (0.574) & 0.155 (0.019) & 0.470 (0.049) & 0.780 (0.030) \\
DevResid  & 0.076 (0.018) & 3.708 (0.518) & 0.166 (0.024) & 0.502 (0.057) & 0.772 (0.049) \\
\bottomrule
\end{tabular}
\end{table}

@@

%\begin{figure}[h]
%	\centering
%	\begin{minipage}[t]{10cm}
%	\begin{algorithm}[H]
%	\caption{Standard Method}
%	\For{k in 1 to K } 
%	{
%		 Fit Cox Regression on $T_{k}$: Obtain model estimates $\hat{\beta}^{-k}$\;
%		 Evaluate the partial likelihood of $\hat{\beta}^{-k}$ on $D_{k}$: $l^{k}(\hat{\beta}^{-k})$\;		
%	} 
%	
%	$ CVE_{st} = - \sum_{k = 1}^{K} l^{k}(\hat{\beta}^{-k})$
% 	\end{algorithm}
%
%	\begin{algorithm}[H]
%  	 \caption{Verweij and Van Houwelingen's Method}
%	\For{k in 1 to K } 
%	{
%		 Fit Cox Regression on $T_{k}$:  Obtain model estimates $\hat{\beta}^{-k}$\;
%		 Evaluate the partial likelihood of $\hat{\beta}^{-k}$ on $T_{k}$: $l^{-k}(\hat{\beta}^{-k})$\;
%		 Evaluate the partial likelihood of $\hat{\beta}^{-k}$ on $D$: $l(\hat{\beta}^{-k})$\;
%		 Take the difference: $ l(\hat{\beta}^{-k}) - l^{-k}(\hat{\beta}^{-k}) $\;
%	} 
%
%	$ CVE_{vvh} = - \sum_{k = 1}^{K} \left\{ l(\hat{\beta}^{-k}) - l^{-k}(\hat{\beta}^{-k}) \right\}$
%	\end{algorithm}
%
%	\begin{algorithm}[H]
%    	\caption{Cross-Validated Linear Predictors}
%	\For{k in 1 to K } 
%	{
%		 Fit Cox Regression on $T_{k}$:  Obtain model estimates $\hat{\beta}^{-k}$\;
%		$\forall$ $ i$ subject in $D_k$: $\hat{\eta}_{i}^{-} = \x_i\hat{\beta}^{-k}$\;
%	} 
%
%	$ CVE_{lp} = - l(\hat{\eta}^{-})$
%	\end{algorithm}
%	
%	\begin{algorithm}[H]
%   	\caption{Sums of Squared Deviance Residuals}
%	\For{k in 1 to K } 
%	{
%		Fit Cox Regression on $T_{k}$:  Obtain model estimates $\hat{\beta}^{-k}$\;
%		$\forall$ $ i$ subject in $D_k$: $\hat{\eta}_{i}^{-} = \x_i\hat{\beta}^{-k}$\;
%	} 
%	Compute baseline hazard $\hat{\Lambda}_{0}$ based on $\hat{\eta}^{-}$\;
%	$\forall$ $ i$ subject $\in \left\{1,2,...,n\right\}$, compute:
%		\par\hspace{0.5cm} $\hat{M_{i}} = \delta_{i} -\hat{\Lambda}_{0}(t_{i})e^{\hat{\eta}^{-}_{i}}$;
%		\par\hspace{0.5cm} $d_{i} = sgn(\hat{M}_{i})(-2(\hat{M}_{i} + \delta_{i}log(\delta_{i} - \hat{M}_{i})))^{1/2}$;
%	$ CVE_{dr} = \sum_{i = 1}^{n} {d}_{i}^2$ \;
%	\end{algorithm}
%	\end{minipage}
%	\caption{Pseudo Code for Cross-validation Procedures}
%	\end{figure}
